Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

The reluctance to adopt chatbots in class might have an explanation: We can
speculate that teaching staff's opinions of chatbots are influenced by negative
experiences with chatbots used in customer support, which is what most people
are likely to have experienced. Further study may be needed to confirm this, but
it is important to keep it in mind when introducing chatbot technologies in the
classroom.  To potentially change this existing perception, it will be necessary
to make chatbots as simple and satisfying to use as possible.

>>>>

The reluctance to adopt chatbots in class might have an explanation: We can
speculate that teaching staff's opinions are influenced by negative
experiences with chatbots used in customer support, which is what most people
are likely to have experienced. Further study may be needed to confirm this, but
it is important to keep it in mind when introducing chatbot technologies in the
classroom.  To potentially change this existing perception, it will be necessary
to make chatbots as simple and satisfying to use as possible.
